The \dealii{} Library, Version 9.4

### 2022-05-26 9.4/paper.tex
Leave a few comments.

The major changes of this release are:
%
\begin{itemize}
  \item Advances in simplex- and mixed-mesh support (see Section~\ref{sec:simplex});
  \item Repartitioning of distributed meshes (see Section~\ref{sec:repartitioning});
  \item Advances in matrix-free infrastructure (see Section~\ref{sec:mf});
  \item Advances in multigrid infrastructure (see Section~\ref{sec:multigrid});
  \item CutFEM support (see Section~\ref{sec:cut});
  \item Performance improvement of particle infrastructure (see Section~\ref{sec:particles});
  \item Two new tutorial programs and a new code gallery program (see Section~\ref{subsec:steps}).
\end{itemize}
%

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii{} release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
%  \item \texttt{AffineConstraints::make\_consistent\_in\_parallel()} allows
%  to make constraints consistent in parallel.
  \item The \texttt{DataOutResample} class does not output a numerical solution 
  on the cells of the original triangulation, but interpolates the result 
  onto a second triangulation (which can be completely unrelated). 
  By using this class, one can output the result obtained on an 
  unstructured mesh on a structured one, which might be a more
  memory-efficient storage format, or one can create a slice in 3D.
  \item The new function \texttt{find\_point\_owner\_rank()} of \texttt{parallel::distributed::Triangulation} allows to find the MPI
  rank of the subdomain of a distributed mesh that contains a given point.
  It is communication-free and leverages the functionality of p4est (>v.2.2).
  Its algorithm is described in \cite{burstedde2020parallel}. Based on the information obtained,
  communication pattern in \texttt{Utilties::MPI::RemotePointEvaluation} can be set up efficiently. Furthermore, this function could be used in the future to allow
  particle simulations where particle movement is not
  limited by CFL conditions, as done in \cite{mirzadeh2016parallel}.
  \item The new function
  \texttt{GridGenerator::pipe\_junction}
  generates a triangulation of three cone-shaped pipes that cross at a bifurcation point in any possible configuration.
  A manifold description will be applied to the boundary, which can be extended into the volume via transfinite interpolation \cite{Gordon82} using the \texttt{TransfiniteInterpolationManifold} class \cite{dealII90}.
  \todo[inline]{[MF] If desired, I can extend this part into its own section of the main chapter. With figures, this would probably occupy about 3/4 of a page.}
\end{itemize}
%
The changelog lists more than 150 other features and bugfixes.

@@

@@

\todo[inline]{Wolfgang to write something about the CA algorithms (and to give
credit to the previous implementation by Peter).}

>>>>

The major changes of this release are:
%
\todo[inline]{Update}
\begin{itemize}
  \item Advances in simplex- and mixed-mesh support (see Section~\ref{sec:simplex});
  \item Repartitioning of distributed meshes (see Section~\ref{sec:repartitioning});
  \item Advances in matrix-free infrastructure (see Section~\ref{sec:mf});
  \item Advances in multigrid infrastructure (see Section~\ref{sec:multigrid});
  \item CutFEM support (see Section~\ref{sec:cut});
  \item Performance improvement of particle infrastructure (see Section~\ref{sec:particles});
  \item Two new tutorial programs and a new code gallery program (see Section~\ref{subsec:steps}).
\end{itemize}
%

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii{} release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
%  \item \texttt{AffineConstraints::make\_consistent\_in\_parallel()} allows
%  to make constraints consistent in parallel.
  \item The \texttt{DataOutResample} class does not output a numerical solution 
  on the cells of the original triangulation, but interpolates the result 
  onto a second triangulation (which can be completely unrelated). 
  By using this class, one can output the result obtained on an 
  unstructured mesh on a structured one, which might be a more
  memory-efficient storage format, or one can create a slice in 3D.
  \item The new function \texttt{find\_point\_owner\_rank()} of \texttt{parallel::distributed::Triangulation} allows to find the MPI
  rank of the subdomain of a distributed mesh that contains a given point.
  It is communication-free and leverages the functionality of p4est (>v.2.2).
  Its algorithm is described in \cite{burstedde2020parallel}. Based on the information obtained,
  communication pattern in \texttt{Utilties::MPI::RemotePointEvaluation} can be set up efficiently. Furthermore, this function could be used in the future to allow
  particle simulations where particle movement is not
  limited by CFL conditions, as done in \cite{mirzadeh2016parallel}.
  \item The new function
  \texttt{GridGenerator::pipe\_junction}
  generates a triangulation of three cone-shaped pipes that cross at a bifurcation point in any possible configuration.
  A manifold description will be applied to the boundary, which can be extended into the volume via transfinite interpolation \cite{Gordon82} using the \texttt{TransfiniteInterpolationManifold} class \cite{dealII90}.
  \todo[inline]{[MF] If desired, I can extend this part into its own
    section of the main chapter. With figures, this would probably
    occupy about 3/4 of a page.}
  \item \todo[inline]{Add something about the FEInterfaceValues improvements.}
\end{itemize}
%
The changelog lists more than 150 other features and bugfixes.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Integration with the Computational Geometry Algorithms
  Library (CGAL)}\label{sec:cgal}

@@

\todo[inline]{Wolfgang to write something about the CA algorithms (and to give
credit to the previous implementation by Peter). Mention improvements
to pack(), unpack(), broadcast() too.}
